Ae. albopictus CPP manuscript

### 2020-02-05 GDDdata_input.Rmd
updated figures

```
```{r}
#adding latitudes
locations<-read.csv("mapping_pops_cpp_expt.csv")
gdd400_us<-left_join(gdd400_us, dplyr::select(locations, pop, latitude, country, only_2008), by=c("pop"))
gdd400_jp<-left_join(gdd400_jp, dplyr::select(locations, pop, latitude, country, only_2008), by=c("pop"))
gdd400_all<-rbind(gdd400_us, gdd400_jp)
gdd400_all$pop<-as.factor(gdd400_all$pop)
gdd400_all<-mutate(gdd400_all, interval=case_when(year<=2017 & year>=2008 ~ 'y2008-2017',
                                                  year<2008 ~ 'y1998-2007'))
```

@@

```
```{r}
ggplot(filter(gdd400_all, only_2008=="n", year!=2018), aes(x=latitude, y=gdd400, color=country)) + scale_color_manual(values=c("black", "gray"), name="Country") + geom_point() + facet_wrap(~year) + xlab("Latitude") + ylab("GDD Deadline (ordinal day)") + theme_bw()

@@

```{r}
field_data<-read.csv("DI_2015_FIELD.csv")
field_data$WeekDate <- reorder(field_data$WeekDate, field_data$Week)
ggplot(field_data, aes(x=WeekDate, y=DI, fill=Eggs)) + geom_point(size=3, shape=21) + scale_fill_manual(values=c("white","grey"), name="Mosquito Population") + theme_bw() + 
theme(legend.position=c(.2,.8), axis.text.x = element_text(angle = 90, hjust = 1)) +
xlab("Week") + ylab("Diapause incidence")

>>>>

```{r}
#adding latitudes
locations<-read.csv("mapping_pops_cpp_expt.csv")
gdd400_us<-left_join(gdd400_us, dplyr::select(locations, pop, latitude, country, only_2008), by=c("pop"))
gdd400_jp<-left_join(gdd400_jp, dplyr::select(locations, pop, latitude, country, only_2008), by=c("pop"))
gdd400_all<-rbind(gdd400_us, gdd400_jp)
gdd400_all$pop<-as.factor(gdd400_all$pop)
gdd400_all<-mutate(gdd400_all, interval=case_when(year<=2017 & year>=2008 ~ 'y2008-2017',
                                                  year<2008 ~ 'y1998-2007'))
```

@@

```
```{r}
ggplot(filter(gdd400_all, only_2008=="n", year!=2018), aes(x=latitude, y=gdd400, fill=country)) + scale_fill_manual(values=c("black", "gray"), name="Country") + geom_point(shape=21) + facet_wrap(~year) + xlab("Latitude") + ylab("GDD Deadline (ordinal day)") + theme_bw() + theme(legend.position="bottom")

@@

```{r}
field_data<-read.csv("DI_2015_FIELD.csv")
field_data$WeekDate <- reorder(field_data$WeekDate, field_data$Week)
ggplot(field_data, aes(x=WeekDate, y=DI, fill=Eggs)) + geom_point(size=3, shape=21) + scale_fill_manual(values=c("white","grey"), name="Mosquito Population") + theme_bw() + 
theme(legend.position=c(.2,.8), axis.text.x = element_text(angle = 90, hjust = 1)) +
xlab("Week") + ylab("Diapause incidence") + geom_vline(aes(xintercept=10.39), linetype="dotted", color="grey") + geom_vline(aes(xintercept=9.99), linetype="dotted", color="black")

### 2020-02-05 MS.Rmd
updated figures

```{r DI_plot, echo=FALSE, include=FALSE}
#plot with DI at 8 h shown as TWO DIFFERENT points (corresponding to two cabinets)
c("PBS", "FEM", "OAK", "JAC", "BRU", "ZIO", "FAY", "NVA", "WAV", "MAN", "BER", "NEW", "OKI", "TAN", "KAG", "YAT", "SAG", "SHI", "YAM", "HIR", "KYO", "TAK", "TOK", "UTS", "KAN", "KHO", "AIZ", "NIG", "SEN", "SAK")
DI_summary$pop<-factor(DI_summary$pop, levels=c("PBS", "FEM", "OAK", "JAC", "BRU", "ZIO", "FAY", "NVA", "WAV", "MAN", "BER", "NEW", "OKI", "TAN", "KAG", "YAT", "SAG", "SHI", "YAM", "HIR", "KYO", "TAK", "TOK", "UTS", "KAN", "KHO", "AIZ", "NIG", "SEN", "SAK"))
DI_plot<-ggplot(DI_summary, aes(x=pp, y=DI, group=pop)) + geom_point() + facet_wrap(~fct_reorder(pop, lat)) + theme_bw() + xlab("Photoperiod (hours)") + ylab("Dipause incidence") 
```

@@

country_DI_bw<-ggplot(filter(DI_short_2, year!=1988), aes(x=lat, y=DI, fill=country, shape=year)) + scale_fill_manual(values=c("black","gray"), name="Country") + scale_shape_manual(values=c(21,24), name="Year") + geom_point(size=3) + theme_bw() + theme(legend.position=c(0.9,0.3), text=element_text(size=14)) + guides(fill = guide_legend(override.aes=list(shape=22))) + xlab("Latitude") + ylab("Short-day diapause incidence")

ggplot(filter(DI_short_2, year!=1988), aes(x=lat, y=DI, color=country, shape=year)) + scale_color_manual(values=c("red","blue")) + geom_point(size=3) + theme_bw() + theme(legend.position=c(0.9,0.3)) + stat_smooth(aes(linetype=year), se=FALSE) + scale_linetype_manual(values=c("dotted","solid")) + xlab("Latitude") + ylab("Short-day diapause incidence")

>>>>

```{r DI_plot, echo=FALSE, include=FALSE}
#plot with DI at 8 h shown as TWO DIFFERENT points (corresponding to two cabinets)
c("PBS", "FEM", "OAK", "JAC", "BRU", "ZIO", "FAY", "NVA", "WAV", "MAN", "BER", "NEW", "OKI", "TAN", "KAG", "YAT", "SAG", "SHI", "YAM", "HIR", "KYO", "TAK", "TOK", "UTS", "KAN", "KHO", "AIZ", "NIG", "SEN", "SAK")
DI_summary$pop<-factor(DI_summary$pop, levels=c("PBS", "FEM", "OAK", "JAC", "BRU", "ZIO", "FAY", "NVA", "WAV", "MAN", "BER", "NEW", "OKI", "TAN", "KAG", "YAT", "SAG", "SHI", "YAM", "HIR", "KYO", "TAK", "TOK", "UTS", "KAN", "KHO", "AIZ", "NIG", "SEN", "SAK"))
DI_plot<-ggplot(DI_summary, aes(x=pp, y=DI, group=pop, fill=country)) + geom_point(shape=21) + facet_wrap(~fct_reorder(pop, lat)) + theme_bw() + xlab("Photoperiod (hours)") + ylab("Dipause incidence") + scale_fill_manual(values=c("black","gray")) + theme(legend.position="NULL")
```

@@

country_DI_bw<-ggplot(filter(DI_short_2, year!=1988), aes(x=lat, y=DI, fill=country, shape=year)) + scale_fill_manual(values=c("black","gray"), name="Country") + scale_shape_manual(values=c(21,24), name="Year") + geom_point(size=3) + theme_bw() + theme(legend.position=c(0.9,0.3), text=element_text(size=14)) + guides(fill = guide_legend(override.aes=list(shape=22))) + xlab("Latitude") + ylab("Short-day diapause incidence") + stat_smooth(aes(linetype=year, color=country), se=FALSE) + scale_linetype_manual(values=c("dotted","solid"), name="Year") + scale_color_manual(values=c("black","gray"), name="Country")

ggplot(filter(DI_short_2, year!=1988), aes(x=lat, y=DI, color=country, shape=year)) + scale_color_manual(values=c("red","blue")) + geom_point(size=3) + theme_bw() + theme(legend.position=c(0.9,0.3)) + stat_smooth(aes(linetype=year, color=country), se=FALSE) + scale_linetype_manual(values=c("dotted","solid")) + xlab("Latitude") + ylab("Short-day diapause incidence")
